---
title: "Attn_habituation_glm"
author: "May Dixon"
date: "September 21, 2016"
output:
  html_document:
    toc: true
    toc_float: true
---

## Three main sections
*initial preference*
*rates of habituation*
*discrimination*



# Initial interest
In this section we are assessing which treatments had the highest initial responses (the most twitches in the first "set" of calls for each treatment per bat)
\


## Initital interest  with generalized linear mixed model (log-linked)
load these libraries: 

```{r, echo=TRUE}
library(lme4)
library(ggplot2)
```
```{r}
 attn_int_2 <- read.table("/Users/maydixon/Dropbox/Attention Project/R/attn_for_initial_interest.txt", header=TRUE) #local
# OR
 # attn_int_2<- read.table("https://raw.githubusercontent.com/maydixon/Attn_Project/master/attn_for_initial_interest_2.7.17.txt", sep="\t", header=TRUE) #on github
        head(attn_int_2)
```

## Model Selection
```{r}
        
        # model: the number of initial twitches is explained by the playback type, with bat id and/ or trial # as a random effect:
        
        initial_int_1 <- glmer(all_tw_set ~ first_stim + (trial_number|Bat_ID), family= "poisson", data = attn_int_2) #model with nested interaction effect/ full model
      
       initial_int_2 <- glmer(all_tw_set ~ first_stim + (1|Bat_ID), family= "poisson", data = attn_int_2) #model with nested interaction effect #
        s_ii1 <- summary(initial_int_1)
        s_ii2 <- summary(initial_int_2)
        s_ii1
        s_ii2
        # So, using AIC, using trial number as a nested random effect with batID is a slightly better model than Bat_ID alone
        #I'll use just the first model initial_int_1 from here on out. 
```
So this model is best:  initial_int_1 <- glmer(all_tw_set ~ trial_name_2 + (trial_number|Bat_ID), family= "poisson", data = attn_int_2) 
   
## Initial interest results
```{r}
        
#continuing to run initial interest with glmer 
        levels(attn_int_2$trial_name_2)
        initial_int_1 <- glmer(all_tw_set ~ first_stim + (trial_number|Bat_ID), family= "poisson", data = attn_int_2) #model with nested interaction effect
        
# running glmer 
# using relevel to find the true value (intercept) for each variable, and what is significantly different from each variable. 
        
        
        attn_int_2$first_stim <- relevel(attn_int_2$first_stim,"De") #MAKE DE REFERENCE
        nlme_int_de_ref<- glmer(all_tw_set ~ first_stim + (trial_number|Bat_ID), family= "poisson", data = attn_int_2)
        summary(nlme_int_de_ref)
        #De is only significantly different than rra (lower)
        
        attn_int_2$first_stim <- relevel(attn_int_2$first_stim,"Ra") #MAKE RA REFERENCE
        nlme_int_ra_ref<- glmer(all_tw_set ~ first_stim + (trial_number|Bat_ID), family= "poisson", data = attn_int_2)
        summary(nlme_int_ra_ref)
        
        attn_int_2$first_stim <- relevel(attn_int_2$first_stim,"Rra") #MAKE RRA REFERENCE
        nlme_int_rra_ref<- glmer(all_tw_set ~ first_stim + (trial_number|Bat_ID), family= "poisson", data = attn_int_2)
        summary(nlme_int_rra_ref)
        
        attn_int_2$first_stim <- relevel(attn_int_2$first_stim,"Rt") #MAKE RT REFERENCE
        nlme_int_rt_ref<- glmer(all_tw_set ~ first_stim + (trial_number|Bat_ID), family= "poisson", data = attn_int_2)
        summary(nlme_int_rt_ref)
        
        attn_int_2$first_stim <- relevel(attn_int_2$first_stim,"Ts") #MAKE Ts REFERENCE
        nlme_int_ts_ref<- glmer(all_tw_set ~ first_stim + (trial_number|Bat_ID), family= "poisson", data = attn_int_2)
        summary(nlme_int_ts_ref)
        
        attn_int_2$first_stim <- relevel(attn_int_2$first_stim,"T1c") #MAKE T1c REFERENCE
        nlme_int_t1c_ref<- glmer(all_tw_set ~ first_stim + (trial_number|Bat_ID), family= "poisson", data = attn_int_2)
        summary(nlme_int_t1c_ref)
        
        attn_int_2$first_stim <- relevel(attn_int_2$first_stim,"T2c") #MAKE T2c REFERENCE
        nlme_int_t2c_ref<- glmer(all_tw_set ~ first_stim + (trial_number|Bat_ID), family= "poisson", data = attn_int_2)
        summary(nlme_int_t2c_ref)
        #
        
        
        #perhaps best order is: Ts, T, Tc, Rt, Rra, Ra, De, can do using relevel() commands from above
```
This falls out into the following result: 

| stim           | value_est |	sig_vals |
| :--------------|-----------|------|
| first_stimDe |	1.67581 |	a |
| first_stimTs |	1.72707 |	a  |
| first_stimT1c|	1.81813 |	a  |
| first_stimRt |	1.83019 |	ab |
| first_stimRa |	1.95817 |	ab |
| first_stimT2c |	2.25382 |	bc |
| first_stimRra |	2.61047 |	c |


Wherein  *stim* are the treatments, *value_est* are the intercept levels- meaning the relative values for the numbers of twitches, and sig_vals denotes which stim are significant'y different, with treatments that are not significantly different sharing letters

## Plotting initial interest
Then plotting those data: 
```{r}
library(plotly)
library(nlme)
library(lme4)
attn_int_2 <- read.table("/Users/maydixon/Dropbox/Attention Project/R/attn_for_initial_interest.txt", header=TRUE) #local
#code for above
 #attn_int_2 <- read.table("/Users/maydixon/Dropbox/Attention Project/R/attn_for_initial_interest_w_na.rm.txt", header=TRUE)
    attn_int_2<-subset(attn_int_2, attn_int_2$bat_name != "Blackbeard") #removes unresponsive bat)
 #find first time experiencing tungara (first), use that
head(attn_int_2)
#how is this variable distributed?
hist(attn_int_2$all_tw_set, breaks=10)
hist(log(attn_int_2$all_tw_set))
#These data look way better when normalized with log
library(ggplot2)


#reordering for plotting: 
      attn_int_2$first_stim <- factor(attn_int_2$first_stim,levels = c("Ts" ,"T1c", "T2c" , "De","Rt" , "Ra" , "Rra"),ordered = TRUE)
      
#perhaps best order is: Ts, T, Tc, Rt, Rra, Ra, De, can do using relevel() commands from above

      #plots
      library(plotly)
      #attn_int_2$md_lg_tw_set<- attn_int_2$md_tw_set + attn_int_2$lg_tw_set
#with logged +1 (for zero) data
p <- ggplot(data = attn_int_2, aes(x = first_stim, y = log(all_tw_set+1), fill=first_stim))
p <- p + geom_boxplot()
p <- p + geom_point(position = position_jitter(width = 0.1))
p <- p + theme(axis.text.x = element_text(angle = 90), legend.position = "none") #format x-axis, and remove side legend
p <- p + xlab("Acoustic stimuli")
p <- p + ylab("log( twitches in first set + 1)")
p
gg<-ggplotly(p)

#look at dots and textures or whatever

#with unlogged data
p <- ggplot(data = attn_int_2, aes(x = first_stim, y = all_tw_set, fill=first_stim))
p <- p + geom_boxplot()
p <- p + theme(axis.text.x = element_text(angle = 90))
p <- p + ylab("twitches in first set")
p + xlab("Acoustic stimuli")
p
```

# Habituation

## Code and models: 


1) a Generalized linear mixed model is better than a general linear mixed model, bc this is technically "count" data and it seems to follow more of a poisson distribution than a normal distribution, dispite the large number of cases. 
2) Use model selection to  formally see whether adding trial number and bat ID as random effects makes the model better, not to mention the relationship between call number and trial name. Would also be good to try trial number as a fixed effect.  

all possible models proposed are built on "substantive sense" based on what is logical in this test, then using AIC and stepwise selection to see which add explanatory power.

* blind stepwise model selection isn't always a good idea, has a tendency to choose more parameterized models. I should start with common sense (why do I think these variables are important?), and then make a few models and then compare them, using AIC, for example. Most likely they won't be radically different
#Possible models:

      #1. twitches ~ call num + call_num:trial_name , random = bat_ID  # main effect of call number and interaction of call and trial, one random
      
      #2. twitches ~ call num + call_num:trial_name , random = bat_ID , trial_number (nested in bat_ID)   # this would remove trial name in and of itself had an impact on twitch number
      #3.  twitches ~ call_num * trial_name random = bat_ID 
      #4.  twitches ~ call_num * trial_name random = bat_ID , trial_number (nested in bat_ID)
      #5.  twitches ~ call_num * trial_name + trial_number random  = bat_ID  #fullest model I think, trial # as main effect 

      #6. all_tw_call ~ call_num*trial_name_2, random = list(Bat_ID=~1 , trial_number= ~1), data= attn_habit_3



```{r}


#make models
#
#attn_habit_3<-read.table("/Users/maydixon/GitHub/Attn_Project/Attn_project_github/attn_habit_1.txt", sep="\t", header=TRUE) #local
#or
attn_habit_3<-read.table("https://raw.githubusercontent.com/maydixon/Attn_Project/master/attn_habit_1.txt", sep="\t", header=TRUE) #web
library(nlme)
library(lme4)
d<- attn_habit_3 
head(d)

 #1 twitches ~ call num + call_num:trial_name , random = bat_ID  # main effect of call number and interaction of call and trial, one random
m1<- glmer(all_tw_call ~ call_num + call_num:trial_name_2 + (1|Bat_ID), data= attn_habit_3, family="poisson")
sm1<- summary(m1)
sm1
#2. twitches ~ call num + call_num:trial_name , random = bat_ID , trial_number (nested in bat_ID)   # this would remove trial name in and of itself had an impact on twitch number
m2<- glmer(all_tw_call ~ call_num + call_num:trial_name_2 + (trial_number| Bat_ID), data= attn_habit_3, family="poisson")
summary(m2)
sm2<- summary(m2)
#2.5 #this adds call number as a main effect, but doesn't include the main effect of trial type
m2_5<- glmer(all_tw_call ~ call_num + call_num:trial_name_2 + trial_number + (1| Bat_ID), data= attn_habit_3, family="poisson")
sm25<- summary(m2_5)
sm25

#past here model fails to converge

#3.  twitches ~ call_num * trial_name random = bat_ID 
m3<- glmer(all_tw_call ~ call_num *trial_name_2  + (1| Bat_ID), data= attn_habit_3, family="poisson")

#4.  twitches ~ call_num * trial_name random = bat_ID , trial_number (nested in bat_ID)
m4<- glmer(all_tw_call ~ call_num *trial_name_2  + (trial_number| Bat_ID), data= attn_habit_3, family="poisson")

#5 twitches ~ call_num * trial_name + trial_number random  = bat_ID  #fullest model I think, trial # as main effect ((WHICH HAS LOWEST AIC?, WHICH MAKES MOST SENSE))
m5<- glmer(all_tw_call ~ call_num *trial_name_2 +trial_number + (1| Bat_ID), data= attn_habit_3, family="poisson") 
```

Ok, so we know that more complex models, any that include trial_name trial_name as a main effect fail to converge. So which of the three models (m1, m2, and m2_5) explains the data best?

I can 1) quickly look at the relative AIC's of each model. The lower AIC's are liable to be better. 2) run partial F tests to test more full models to more reduced models. 

Comparing AIC:
```{r}
#comparing AIC's of each model
AIC_comp<-cbind(sm1$AICtab, sm2$AICtab, sm25$AICtab)
colnames(AIC_comp)<-(c("sm1", "sm2", "sm25"))
AIC_comp
```

So model 2 has the lowest AIC. Is it significantly better? Can run a partial F test: 
```{r}
#nested F test to test models. 
anova(m2_5, m2,  test="F") #compares the reduced model trial name as a random factor to full model with trial_name as main effect
# I think that this shows that model 2 has more explanatory power
anova(m1, m2, test = "F")

# model 2 has the most explanatory power. 


```

So, it seems that model #2 explains the data best: [ twitches ~ call num + call_num:trial_name , random = bat_ID , trial_number (nested in bat_ID) ]


That said, what does model 2 tell us? 

```{r}

sm2
sm2$coefficients
sm2$coefficients[1,1]

```
This is the estimate for the slope of responses to dendropsophes. It is different than tungara complex, but not different than anything else

So, the way to interpret this is: 
The *intercept* is the number of twitches at call 0, for whatever the reference is. Pretty similar for all the treatments. 
The *slope* value for call number is the main effect of change in the number of twitches with time, with all the differences compared against the reference value. 

To find the slopes of each of the other treatments and how they differ from call number, add the interaction effect to the effect for call number to get the true value. Relevel to get the one that is the current reference. 

To see whether there is a significant difference between treatments, relevel, and see what the values are. These are kind of complicated with glmm, so don't read into them everything. 

This is a sheet with a summary of the slopes of the results:

```{r}

#making a little sheet to store results # Don't run again, I just scrolled through manually
#tmts<- c("call_num", "de", "ra", "rra", "rt", "t_de", "t_ra", "tc", "tia", "ts")
attn_habit_3$trial_name_2 <- relevel(attn_habit_3$trial_name_2,"de_t_de") #MAKE DE REFERENCE
m2<- glmer(all_tw_call ~ call_num + call_num:trial_name_2 + (trial_number| Bat_ID), data= attn_habit_3, family="poisson") #run model
sm2<- summary(m2)  #make summary
slope_coeff<- c(sm2$coefficients[,1]) #grab row with the coefficients
slope_est <- slope_coeff + (sm2$coefficients[2,1]) #add the interactions to call# coeff
slopes <- cbind(slope_coeff, slope_est) #make into a sheet
slopes<- slopes[3:10,] #remove the first two rows that don't make sense
attn_habit_3$trial_name_2 <- relevel(attn_habit_3$trial_name_2,"ra_t_ra") #MAKE RA REFERENCE so that DE interaction coefficients show in output
m2a<- glmer(all_tw_call ~ call_num + call_num:trial_name_2 + (trial_number| Bat_ID), data= attn_habit_3, family="poisson") #run model again
sm2a<- summary(m2a)  #make summary
de_coeff_est<-  c(sm2a$coefficients[3,1]) #pull de coefficient
de_slope_est<- de_coeff_est+ sm2a$coefficients[2,1]  #add call num to de coefficient
de_row<- cbind(de_coeff_est, de_slope_est) #put into row
slopes<-rbind(slopes, de_row) #add de row to rest of it 
rownames(slopes) [9] <- "call_num:trial_name_2de_t_de" #add the de row name

slopes #returns the slope estimations (in the second row, for each of the treatments)
 #So, which are significantly different?
 #copying and pasting into an excel doc. 
```

This is s series of "relevels" to show which slopes are significantly different from each other according to this model. To run, simply run the line with the relevel function of the treatment you would like to make reference, and then run the line with the model and summary: 
```{r}
#relevel lines
#DE as reference:
attn_habit_3$trial_name_2 <- relevel(attn_habit_3$trial_name_2,"de_t_de") 
#RA as reference: 
attn_habit_3$trial_name_2 <- relevel(attn_habit_3$trial_name_2,"ra_t_ra") 
#RRA as reference:
attn_habit_3$trial_name_2 <- relevel(attn_habit_3$trial_name_2,"rra_rt_rra") 
#TS as reference:
attn_habit_3$trial_name_2 <- relevel(attn_habit_3$trial_name_2,"ts_tc_ts") 
#TIA as reference:
attn_habit_3$trial_name_2 <- relevel(attn_habit_3$trial_name_2,"tia_tib_tia") 
#TC as reference:
attn_habit_3$trial_name_2 <- relevel(attn_habit_3$trial_name_2,"tc_ts_tc")
#T_RA as reference:
attn_habit_3$trial_name_2 <- relevel(attn_habit_3$trial_name_2,"t_ra_t")
#T_DE as reference:
attn_habit_3$trial_name_2 <- relevel(attn_habit_3$trial_name_2,"t_de_t")
#RT as reference:
attn_habit_3$trial_name_2 <- relevel(attn_habit_3$trial_name_2,"rt_rra_rt")


#model running lines:
m2<- glmer(all_tw_call ~ call_num + call_num:trial_name_2 + (trial_number| Bat_ID), data= attn_habit_3, family="poisson") #run model
sm2<- summary(m2)  #make summary
sm2

```

## Habituation results summary

So, the below table shows all the the treatments with their slopes, from biggest to smallest, and their tests of significant difference  tests (all ***) denoted by letters. If two treatments share a letter, they were not significantly different (1), and if they do, they were significantly different (0): 

| trial_name |	slope_coeff |	slope_est |	sig.dif
|:---------------------------|-----------|------------|-----|
| call_num:trial_name_2de_t_de |	0.45847131 |	-0.07455272 |	a |
| call_num:trial_name_2tc_ts_tc |	-0.00334758 |	-0.07790228 |a |
| call_num:trial_name_2t_de_t |	-0.10200029 |	-0.17655499 |	b |
| call_num:trial_name_2tia_tib_tia |	-0.11624862 |	-0.19080332 |	b |
| call_num:trial_name_2t_ra_t |	-0.13224066 |	-0.20679536 |	b |
| call_num:trial_name_2rt_rra_rt |	-0.13963957 |	-0.21419427 |	b |
| call_num:trial_name_2ts_tc_ts |	-0.14339025 |	-0.21794495 |	b |
| call_num:trial_name_2rra_rt_rra |	-0.27034559 |	-0.34490029 |	c |
| call_num:trial_name_2ra_t_ra |	-0.45847568 |	-0.53303038 |	d |

   *organization of this table can be found in glmer_results_summaries.xls excel sheet
   
So, the bats habituated most slowly to the DE and The TC, which makes sense, becuase each of these is quite attractive, and the bats are less likely to be habituated. No difference in the amount that they habituated to DE and TC

bats habituated to all the simpler tungaras at the same rate (sanity check)

Bats habituted to RRA very quickly, and habituated fastest to the regular rhinella alata. 

So, they did habituate fastest to calls that were less biologically relevent to them. 






## Habituation plots, various: 

```{r}
library(ggplot2)
    # New habituation plots (boxplots)
        
        ## can i make a plot of boxplots for each trial type, all the way across trial?
        attn_whole<-read.table("https://raw.githubusercontent.com/maydixon/Attn_Project/master/attention_Rcopy_individuals_condensed.txt", sep="\t", header=TRUE)
        attn_whole <- subset(attn_whole, attn_whole$bat_name != "Blackbeard") 
        # want just one line for each "set"
        #pull partial string match  x.1 for call number using grep
        attn_whole_set <- attn_whole[grep(".1", attn_whole$call_num), ]
        attn_whole_set_1to5 <- subset(attn_whole_set, attn_whole_set$set_num != "6" & attn_whole_set$set_num != "7") #removing last 2 sets
        
        
        #all treatments together, overall trend
        
        p_all<-ggplot(data=attn_whole_set_1to5, aes(x = set_num, group=set_num , y = all_tw_set, fill=set_num))      #
        p_all <- p_all + geom_boxplot()
        p_all <- p_all + ylab("Twitches in presentation")
        p_all <- p_all + xlab("presentation number")
        p_all <- p_all + ggtitle("All")
        p_all
        
        
        #making a plot for the entire of one treatment, with each set getting a boxplot
        
        #DE
        de_data<- attn_whole_set_1to5[attn_whole_set_1to5$trial_name_2=="de_t_de", ]       
        p_de <-ggplot(data=de_data, aes(x = set_num, y = all_tw_set))      
        p_de <- p_de + geom_boxplot(aes(fill=factor(set_num)))
        p_de <- p_de + guides(fill=FALSE)
        p_de <- p_de + scale_x_continuous(breaks = c(1,2,3,4,5,6,7)) +
              scale_fill_manual(breaks = c("1", "2", "3", "4", "5", "6", "7"),
                                values=c("#F966D5", "#F966D5", "#F966D5", "#F966D5", "#F966D5", "#C39921", "#F966D5"))
        p_de <- p_de + ylab("Twitches in presentation")
        p_de <- p_de + xlab("presentation number")
        p_de<- p_de + labs(title = "D. ebraccatus / P. pustulosus")
        p_de <- p_de + coord_cartesian(ylim = c(0, 25))
        p_de <- p_de + stat_smooth(colour="black", size=0.5, method="lm", se=FALSE ,  data= subset(de_data, de_data$set_num!="6" & de_data$set_num!="7")) 
        p_de
        #try<-subset(de_data, de_data$set_num!="6" & de_data$set_num!="7")
        #View(try)
        #made using coloring advice from "http://stackoverflow.com/questions/10805643/ggplot2-add-color-to-boxplot-continuous-value-supplied-to-discrete-scale-er"
        
        
        
        
        
        ### very variable, eh? should check that
        d1<- attn_whole_set_1to5[attn_whole_set_1to5$trial_name_2=="de_t_de", ]
        plot(d1$Bat_ID, d1$all_tw_set )
        #for Rra
        hist(d1$all_tw_set)
        
        
        #t_de
        t_de_data <- attn_whole_set_1to5[attn_whole_set_1to5$trial_name_2=="t_de_t", ]
        p_t_de <-ggplot(data=t_de_data, aes(x = set_num, y = all_tw_set))      
        p_t_de <- p_t_de + geom_boxplot(aes(fill=factor(set_num)))
        p_t_de <- p_t_de + guides(fill=FALSE)
        p_t_de <- p_t_de + scale_x_continuous(breaks = c(1,2,3,4,5,6,7)) +
              scale_fill_manual(breaks = c("1", "2", "3", "4", "5", "6", "7"),
                                values=c( "#C39921", "#C39921", "#C39921", "#C39921", "#C39921", "#F966D5", "#C39921"))
        p_t_de <- p_t_de + ylab("Twitches in presentation")
        p_t_de + xlab("presentation number")
        p_t_de <- p_t_de + xlab("presentation number")
        p_t_de<- p_t_de + labs(title = "P. pustulosus / D. ebraccatus")
        p_t_de<- p_t_de + coord_cartesian(ylim = c(0, 25))
        p_t_de <- p_t_de + stat_smooth(colour="black", size=0.5, method="lm", se=FALSE ,  data= subset(t_de_data, t_de_data$set_num!="6" & t_de_data$set_num!="7")) 
        p_t_de
        
        
        #rra
        rra_data<- attn_whole_set_1to5[attn_whole_set_1to5$trial_name_2=="rra_rt_rra", ]
        p_rra <-ggplot(data=rra_data, aes(x = set_num, y = all_tw_set))      
        p_rra <- p_rra + geom_boxplot(aes(fill=factor(set_num)))
        p_rra <- p_rra + guides(fill=FALSE)
        #P_rra<- p_rra + coord_cartesian(ylim = c(0, 20)
        p_rra <- p_rra + scale_x_continuous(breaks = c(1,2,3,4,5,6,7)) +
              scale_fill_manual(breaks = c("1", "2", "3", "4", "5", "6", "7"),
                                values=c( "#1EB7E9","#1EB7E9", "#1EB7E9","#1EB7E9","#1EB7E9","#1EBF95","#1EB7E9" ))
        p_rra <- p_rra + ylab("Twitches in presentation")
        p_rra + xlab("presentation number")
        p_rra <- p_rra + xlab("presentation number")
        p_rra<- p_rra + labs(title="Reversed R. alata / Reversed P. pustulosus")
        p_rra<- p_rra  + coord_cartesian(ylim = c(0, 25))
        p_rra <- p_rra + stat_smooth(colour="black", size=0.5, method="lm", se=FALSE ,  data= subset(rra_data, rra_data$set_num!="6" & rra_data$set_num!="7")) 
        p_rra
        
        
        #ra
        ra_data<- attn_whole_set_1to5[attn_whole_set_1to5$trial_name_2=="ra_t_ra", ]
        p_ra <-ggplot(data=ra_data, aes(x = set_num, y = all_tw_set))      
        p_ra <- p_ra + geom_boxplot(aes(fill=factor(set_num)))
        p_ra <- p_ra + guides(fill=FALSE)
        p_ra <- p_ra + scale_x_continuous(breaks = c(1,2,3,4,5,6,7)) +
              scale_fill_manual(breaks = c("1", "2", "3", "4", "5", "6", "7"),
                                values=c( "#A58DFC", "#A58DFC","#A58DFC","#A58DFC","#A58DFC", "#C39921", "#A58DFC" ))
        p_ra <- p_ra + ylab("Twitches in presentation")
        p_ra + xlab("presentation number")
        p_ra <- p_ra + xlab("presentation number")
        p_ra<- p_ra + labs(title="R. alata / P. pustulosus")
        p_ra<- p_ra + coord_cartesian(ylim = c(0, 25)) #sets y limit
        p_ra <- p_ra + stat_smooth(colour="black", size=0.5, method="lm", se=FALSE ,  data= subset(ra_data, ra_data$set_num!="6" & ra_data$set_num!="7")) 
        
        p_ra
        
        
        
        #t_ra
        t_ra_data <- attn_whole_set_1to5[attn_whole_set_1to5$trial_name_2=="t_ra_t", ]
        p_t_ra <-ggplot(data=t_ra_data, aes(x = set_num, y = all_tw_set))      
        p_t_ra <- p_t_ra + geom_boxplot(aes(fill=factor(set_num)))
        p_t_ra <- p_t_ra + guides(fill=FALSE)
        p_t_ra <- p_t_ra + scale_x_continuous(breaks = c(1,2,3,4,5,6,7)) +
              scale_fill_manual(breaks = c("1", "2", "3", "4", "5", "6", "7"),
                                values=c(  "#C39921", "#C39921", "#C39921", "#C39921", "#C39921","#A58DFC","#C39921" ))
        p_t_ra <- p_t_ra + ylab("Twitches in presentation")
        p_t_ra + xlab("presentation number")
        p_t_ra <- p_t_ra + xlab("presentation number")
        p_t_ra<- p_t_ra + labs(title="P. pustulosus / R. alata")
        p_t_ra<- p_t_ra + coord_cartesian(ylim = c(0, 25)) #sets y limit
        p_t_ra <- p_t_ra + stat_smooth(colour="black", size=0.5, method="lm", se=FALSE ,  data= subset(t_ra_data, t_ra_data$set_num!="6" & t_ra_data$set_num!="7")) 
        p_t_ra
        
        #rt
        rt_data<- attn_whole_set_1to5[attn_whole_set_1to5$trial_name_2=="t_ra_t", ]
        p_rt <-ggplot(data=rt_data, aes(x = set_num, y = all_tw_set))      
        p_rt <- p_rt + geom_boxplot(aes(fill=factor(set_num)))
        p_rt <- p_rt + guides(fill=FALSE)
        p_rt <- p_rt + scale_x_continuous(breaks = c(1,2,3,4,5,6,7)) +
              scale_fill_manual(breaks = c("1", "2", "3", "4", "5", "6", "7"),
                                values=c( "#1EBF95","#1EBF95", "#1EBF95", "#1EBF95", "#1EBF95","#1EB7E9", "#1EBF95" ))
        p_rt <- p_rt + ylab("Twitches in presentation")
        p_rt + xlab("presentation number")
        p_rt <- p_rt + xlab("presentation number")
        p_rt<- p_rt + labs(title="Reversed P. pustulosus / Reversed R. alata")
        p_rt<- p_rt + coord_cartesian(ylim = c(0, 25)) #sets y limit
        p_rt <- p_rt + stat_smooth(colour="black", size=0.5, method="lm", se=FALSE ,  data= subset(rt_data, rt_data$set_num!="6" & rt_data$set_num!="7")) 
        p_rt
        
        
        #tc
        tc_data<- attn_whole_set_1to5[attn_whole_set_1to5$trial_name_2=="tc_ts_tc", ]
        p_tc <-ggplot(data=tc_data, aes(x = set_num, y = all_tw_set))      
        p_tc <- p_tc + geom_boxplot(aes(fill=factor(set_num)))
        p_tc <- p_tc + guides(fill=FALSE)
        p_tc <- p_tc + scale_x_continuous(breaks = c(1,2,3,4,5,6,7)) +
              scale_fill_manual(breaks = c("1", "2", "3", "4", "5", "6", "7"),
                                values=c( "#57B21F", "#57B21F","#57B21F","#57B21F","#57B21F", "#F67770", "#57B21F" ))
        p_tc <- p_tc + ylab("Twitches in presentation")
        p_tc + xlab("presentation number")
        p_tc <- p_tc + xlab("presentation number")
        p_tc<- p_tc + labs(title="3 chuck P. pustulosus / simple P. pustulosus")
        p_tc<- p_tc + coord_cartesian(ylim = c(0, 25)) #sets y limit
        p_tc <- p_tc + stat_smooth(colour="black", size=0.5, method="lm", se=FALSE ,  data= subset(tc_data, tc_data$set_num!="6" & tc_data$set_num!="7")) 
        p_tc
        
        #ts
        ts_data<- attn_whole_set_1to5[attn_whole_set_1to5$trial_name_2=="ts_tc_ts", ]
        p_ts <-ggplot(data=ts_data, aes(x = set_num, y = all_tw_set))      
        p_ts <- p_ts + geom_boxplot(aes(fill=factor(set_num)))
        p_ts <- p_ts + guides(fill=FALSE)
        p_ts <- p_ts + scale_x_continuous(breaks = c(1,2,3,4,5,6,7)) +
              scale_fill_manual(breaks = c("1", "2", "3", "4", "5", "6", "7"),
                                values=c("#F67770", "#F67770", "#F67770", "#F67770", "#F67770",  "#57B21F", "#F67770" ))
        p_ts <- p_ts + ylab("Twitches in presentation")
        p_ts + xlab("presentation number")
        p_ts <- p_ts + xlab("presentation number")
        p_ts<- p_ts + labs(title="Simple P. pustulosus / 3 chuck P. pustulosus")
        p_ts<- p_ts + coord_cartesian(ylim = c(0, 25)) #sets y limit
        p_ts <- p_ts + stat_smooth(colour="black", size=0.5, method="lm", se=FALSE ,  data= subset(ts_data, ts_data$set_num!="6" & ts_data$set_num!="7")) 
        p_ts
        
        #tia_tib_tia
        tia_data <- attn_whole_set_1to5[attn_whole_set_1to5$trial_name_2=="tia_tib_tia", ]
        p_tia <-ggplot(data=tia_data, aes(x = set_num, y = all_tw_set))      
        p_tia <- p_tia + geom_boxplot(aes(fill=factor(set_num)))
        p_tia <- p_tia + guides(fill=FALSE)
        p_tia <- p_tia + scale_x_continuous(breaks = c(1,2,3,4,5,6,7)) +
              scale_fill_manual(breaks = c("1", "2", "3", "4", "5", "6", "7"),
                                values=c("#AD881D", "#AD881D","#AD881D","#AD881D","#AD881D", "#DEB339", "#AD881D" )) #using 2 tints of the standard yellow
        p_tia <- p_tia + ylab("Twitches in presentation")
        p_tia + xlab("presentation number")
        p_tia <- p_tia + xlab("presentation number")
        p_tia<- p_tia + labs(title="Tungara individuals contrast")
        p_tia<- p_tia + coord_cartesian(ylim = c(0, 25)) #sets y limit
        p_tia <- p_tia + stat_smooth(colour="black", size=0.5, method="lm", se=FALSE ,  data= subset(tia_data, tia_data$set_num!="6" & tia_data$set_num!="7"))
        p_tia
        
        
        # Multiple plot function
#
# ggplot objects can be passed in ..., or to plotlist (as a list of ggplot objects)
# - cols:   Number of columns in layout
# - layout: A matrix specifying the layout. If present, 'cols' is ignored.
#
# If the layout is something like matrix(c(1,2,3,3), nrow=2, byrow=TRUE),
# then plot 1 will go in the upper left, 2 will go in the upper right, and
# 3 will go all the way across the bottom.
#
multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  require(grid)

  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)

  numPlots = length(plots)

  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                    ncol = cols, nrow = ceiling(numPlots/cols))
  }

 if (numPlots==1) {
    print(plots[[1]])

  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))

    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))

      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}
        multiplot(p_ra, p_t_ra, p_rra, p_rt, p_de, p_t_de, p_ts, p_tc, p_tia )
      
```




```{r, echo=FALSE}
attn_habit_3<-read.table("https://raw.githubusercontent.com/maydixon/Attn_Project/master/attn_habit_1.txt", sep="\t", header=TRUE)
        #View(attn_habit_3)
        str(attn_habit_3) #there is a lot in here I'm not using now
        #glm for all twitches with an interaction between call number and trial name as main effect, bat ID as random effect, for all twitches
        library(nlme)
```

  
   
   
# Discrimination

The following are all the tests for discimination. In each of the following trials, we are comparing the response to the 5th set to the 6th set (the discrimination stimulus), and the 7th set (the dishabituation simulus). A significantly greater response to the 6th or 7th set from the 5th set is indicative of discrimination between the stimuli. In all cases the response was the total number of ear twitches. 
     
To analyze these, I used linear mixed models with the following model: 
     
       *total twitches ~ set number , random = bat*

      (I used trial_number in other models in this analysis, but it did not explain more of the variance in this case)
      


##quickie summary chart version: 

| trial_name | descrim? |dishabit? | comments
|:----------|------|------|-------------------------------------------|
|de_t_de  | no | no | probably bc no habituation in first place |
|t_de_t | no |no | probably bc high overall responses, low habit |
|ra_t_ta |yes, strong | yes | model failed to converge tho |
|t_ra_t | no | no | model didn't converge, failed hessian? |
|rra_rt_rra | yes, strong | no |  |
|rt_rra_rt | yes | no |  |
|tc_ts_tc |no |no |  crazy outlier to deal with, nothing either way, possibly no habituation|
|ts_tc_ts | yes | no | more clear bc better habituation|
| tia_tib_tia | no | no | not even at all. should have habituated too |

##Discrimination stats      
      
```{r, include=FALSE}

######################

#import data, remove duds, remove bad treatments
 attention_Rcopy_individuals_condensed <- read.delim("https://raw.githubusercontent.com/maydixon/Attn_Project/master/attention_Rcopy_individuals_condensed.txt", header=TRUE) #this file has all sets, and a row with condensed Tia_tib_Tia
#or local
attention_Rcopy_individuals_condensed <- read.table("/Users/maydixon/GitHub/Attn_Project/Attn_project_github/attention_Rcopy_individuals_condensed.txt", header=TRUE )

attention_Rcopy1<- subset(attention_Rcopy_individuals_condensed, attention_Rcopy_individuals_condensed$bat_name != "Blackbeard" ) #removes unresponsive bat
attention_Rcopy2<-subset(attention_Rcopy1, attention_Rcopy1$trial_name != "t_rt_t" & attention_Rcopy1$trial_name != "rt_t_rt") #removes variables only tested on one bat
 attn_r2 <- attention_Rcopy2 #short same version
#pull partial string match  x.1 for call number using grep
        
attn_set <- attn_r2[grep(".1", attn_r2$call_num), ]
#View(attn_set)
```
 


```{r, include= FALSE }
#2 need to subset data to refer to one treatment at a time
unique(attn_set$trial_name_2)

subset_de <- subset(attn_set, attn_set$trial_name_2=="de_t_de")
subset_ra <- subset(attn_set, attn_set$trial_name_2=="ra_t_ra")
subset_rra <- subset(attn_set, attn_set$trial_name_2=="rra_rt_rra")
subset_rt <- subset(attn_set, attn_set$trial_name_2=="rt_rra_rt")
subset_t_de <- subset(attn_set, attn_set$trial_name_2=="t_de_t")
subset_t_ra <- subset(attn_set, attn_set$trial_name_2=="t_ra_t")
subset_tc <- subset(attn_set, attn_set$trial_name_2=="tc_ts_tc")
subset_tia <- subset(attn_set, attn_set$trial_name_2=="tia_tib_tia")
subset_ts <- subset(attn_set, attn_set$trial_name_2=="ts_tc_ts")

#further subset to only include sets 5, 6, 7
subset_de1 <- subset(subset_de, subset_de$set_num=="5" | subset_de$set_num=="6" | subset_de$set_num=="7" )
subset_ra1 <- subset(subset_ra, subset_ra$set_num=="5" | subset_ra$set_num=="6" | subset_ra$set_num=="7" ) 
subset_rra1 <- subset(subset_rra, subset_rra$set_num=="5" | subset_rra$set_num=="6" | subset_rra$set_num=="7" )
subset_rt1 <- subset(subset_rt, subset_rt$set_num=="5" | subset_rt$set_num=="6" | subset_rt$set_num=="7" )
subset_t_de1 <- subset(subset_t_de, subset_t_de$set_num=="5" | subset_t_de$set_num=="6" | subset_t_de$set_num=="7" )
subset_t_ra1 <- subset(subset_t_ra, subset_t_ra$set_num=="5" | subset_t_ra$set_num=="6" | subset_t_ra$set_num=="7" )
subset_tc1 <- subset(subset_tc, subset_tc$set_num=="5" | subset_tc$set_num=="6" | subset_tc$set_num=="7" )
subset_tia1 <- subset(subset_tia, subset_tia$set_num=="5" | subset_tia$set_num=="6" | subset_tia$set_num=="7" )
subset_ts1 <- subset(subset_ts, subset_ts$set_num=="5" | subset_ts$set_num=="6" | subset_ts$set_num=="7" )

#load library
library(nlme)
library(lme4)
#set working directory if running on wherever
#setwd("~/Dropbox/Attention Project/R/Sessions/09.26.16")        
# run one of the lme
# Model should be twitches per set ~ set num * treatment , random= batid #(trial number does not add explanatoryness)
```

### *D. ebracattus* v Tungara: 
normality of data:
```{r, echo= FALSE}
qqnorm(subset_de1$all_tw_set)

```


Results of linear mixed model: This models asks whether there is a significant difference between set 5 & 6, and 5 & 7. 

```{r, echo=FALSE}
#de_desc<- lme(all_tw_set ~ as.factor(set_num), random = ~1|Bat_ID, data = subset_de1) # use as.factor so model sees these as factors
de_desc_glm <- glmer(all_tw_set ~ as.factor(set_num) + (1|Bat_ID) , data = subset_de1, family= "poisson")

```
```{r}
#summary(de_desc)
summary(de_desc_glm)
de_t_de_desc <- boxplot(all_tw_set ~ (as.factor(set_num)), main = "de_t_de", data=subset_de1)

```


So, there is no evidence of discrimination between ebracattus and tungara. This may be because there was no habituation to D. ebracattus (actually there was slight sensitization)       


### *Rhinella alata* v Tungara
normality of data: 
```{r}
qqnorm(subset_ra1$all_tw_set)
```
```{r, include=FALSE}
#ra_desc<- lme(all_tw_set ~ as.factor(set_num), random = ~1|Bat_ID, data = subset_ra1) # use as.factor so moral sees these as factors
ra_desc_glm <- glmer(all_tw_set ~ as.factor(set_num) + (1|Bat_ID) , data = subset_ra1, family= "poisson")
```
```{r}
summary(ra_desc_glm)
#boxplot
ra_descrim_plot<- boxplot(all_tw_set ~ (as.factor(set_num)), main = "ra_t_ra", data=subset_ra1)
```

There is evidence for descrimination between rhinella alata and tungara frogs

### Reversed *R. alata* v tungara

Normality of data:
```{r}
qqnorm(subset_rra1$all_tw_set)
```
```{r, include=FALSE}
rra_desc_glm <- glmer(all_tw_set ~ as.factor(set_num) + (1|Bat_ID) , data = subset_rra1, family= "poisson")

#rra_desc<- lme(all_tw_set ~ as.factor(set_num), random = ~1|Bat_ID, data = subset_rra1) # use as.factor so morral sees these as factors
```
```{r}
#summary(rra_desc)
summary(rra_desc_glm)
#boxplot
boxplot(all_tw_set ~ (as.factor(set_num)), main = "rra_rt_rra", data=subset_rra1)
```

There is evidence for descrimination between 5 and 6, but not for dishabituation (5 and 7). There was very steep habituation to reversed rhinella alata, which might explain a part of this trend. 

So, clearly they discriminate / can discriminate to the sounds of the reversed rhinella and the reversed tungara. 


### reversed tungara v reversed *R. alata*

Normality of data: 
```{r, echo=FALSE}
qqnorm((subset_rt1$all_tw_set))
```

This linear mixed model may not be appropriate for this test given its right-skewed distribution

```{r, echo=FALSE}
#rt_desc<- lme(all_tw_set ~ as.factor(set_num), random = ~1|Bat_ID, data = subset_rt1) # use as.factor so mortl sees these as factors
rt_desc_glm <- glmer(all_tw_set ~ as.factor(set_num) + (1|Bat_ID) , data = subset_rt1, family= "poisson")


```
``````{r}
summary(rt_desc_glm)
#boxplot
boxplot(all_tw_set ~ (as.factor(set_num)), main = "rt_rra_rt", data=subset_rt1)
#logged boxplot:

rt_desc_transformed<-boxplot((log(all_tw_set+1)) ~ (as.factor(set_num)), main = "rt_rra_rt log transformed", data=subset_rt1)
```


So again, there is discrimination, if not dishabituation between reversed tungara and reversed alata. 


### Tungara v *D. ebracattus*

```{r, echo=FALSE}
qqnorm(subset_t_de1$all_tw_set)
#  Should be twitches/set ~set num*treatment t_dendom= batid #trial number does not add explanatoryness
#t_de_t_desc<- lme(all_tw_set ~ as.factor(set_num), random = ~1|Bat_ID, data = subset_t_de1) # use as.factor so mot_del sees these as factors
#boxplot
t_de_desc_glm <- glmer(all_tw_set ~ as.factor(set_num) + (1|Bat_ID) , data = subset_t_de1, family= "poisson")

summary(t_de_desc_glm)
#boxplot
t_de_t_desc_plot<- boxplot(all_tw_set ~ (as.factor(set_num)), main = "t_de_t", data=subset_t_de1)
```

There is no evidence for descrimination between tungara and dendrobates Perhaps/ likley due to high overall responses

###Tungara v R. alata
```{r, echo=FALSE}

#remember to reset relevel if running this again
qqnorm(subset_t_ra1$all_tw_set) 
hist(subset_t_ra1$all_tw_set)
#maybe can't justify normal dist
#t_ra_t_desc<- lme(all_tw_set ~ as.factor(set_num), random = ~1|Bat_ID, data = subset_t_ra1) # use as.factor so  sees these as factors

t_ra_t_desc_glm <- glmer(all_tw_set ~ as.factor(set_num) + (1|Bat_ID) , data = subset_t_ra1, family= "poisson")
#not converging?
summary(t_ra_t_desc_glm)
#boxplot
t_ra_t_desc_plot<-boxplot(all_tw_set ~ (as.factor(set_num)), main = "t_ra_t", data=subset_t_ra1)


```
####*** Probably not converging bc the ra is so close to 0 (hessian boundry?)
## return to this to troubleshoot. 

No discimination between treatments detected. 

#### Use relevel to see whether there is a difference between set 6 and 7
```{r, echo=FALSE}



subset_t_ra1$set_num <- relevel(as.factor(subset_t_ra1$set_num), ref="6")
t_ra_t_desc_2<- lme((sqrt(all_tw_set)) ~ as.factor(set_num), random = ~1|Bat_ID, data = subset_t_ra1) # releveled lme
summary(t_ra_t_desc_2)
```

. 

## Intraspecific Trials

## Complex tungara v simple tungara
```{r}

qqnorm(subset_tc1$all_tw_set)
#one total outlier (what should I do about that?)
tc_desc_glm <- glmer(all_tw_set ~ as.factor(set_num) + (1|Bat_ID) , data = subset_tc1, family= "poisson")
summary(tc_desc_glm)
# boxplot
tc_ts_tc_plot<- boxplot(all_tw_set ~ (as.factor(set_num)), main = "tc_ts_tc", data=subset_tc1)

#dealing with outlier
#View(subset_tc1)
subset_tc1$all_tw_set.no<-subset_tc1$all_tw_set
subset_tc1$all_tw_set.no <- ifelse(subset_tc1$all_tw_set.no > 15, NA, subset_tc1$all_tw_set.no) #removing points over 15
tc_ts_tc_plot.no<- boxplot(all_tw_set.no ~ (as.factor(set_num)), main = "tc_ts_tc", data=subset_tc1)
tc_desc_glm.no <- glmer(all_tw_set.no ~ as.factor(set_num) + (1|Bat_ID) , data = subset_tc1, family= "poisson")
summary(tc_desc_glm.no)
#makes nothing significant at all. Diff between last 2? 
```


There is no apparent discrimination between complex and simple calls in this test. However, there is an outlier that could easily be messing with this. Outlier doesn't change the relationship. It just makes them all the more the same

If this is accurate, it is probable that discrimination is obscured by simple calls being less salient stimuli, so the interuption in habituation is masked by lower overall interest in the simple call. See the inverse treatment:

##Simple tungara against complex tungara call
```{r}

qqnorm(subset_ts1$all_tw_set)
hist(subset_ts1$all_tw_set)
#looks oookay (pretty 0 weighted)
ts_desc_glm <- glmer(all_tw_set ~ as.factor(set_num) + (1|Bat_ID) , data = subset_ts1, family= "poisson")
#ts_desc<- lme(all_tw_set ~ as.factor(set_num), random = ~1|Bat_ID, data = subset_ts1) # use as.factor so  sees these as factors
summary(ts_desc_glm)
# boxplot
ts_tc_ts_plot<- boxplot(all_tw_set ~ (as.factor(set_num)), main = "ts_tc_ts", data=subset_ts1)    

```

This shows that bats discriminate between complex and simple tungara calls (0c v 2c). There is clear evidence of discrimination, but not of dishabituation  Note how discrimination is more apparent when the less salient stimulus is the one that is being habituated. ((Also, more habituation=more evidence of discrimination))

## Tungara "A" v Tungara "B" (or the id of individuals trials)

```{r}

qqnorm(subset_tia1$all_tw_set)
# not justifiably normal (left/0 skewed)
#tia_desc<- lme(all_tw_set ~ as.factor(set_num), random = ~1|Bat_ID, data = subset_tia1) # use as.factor so  sees these as factors
tia_desc_glm <- glmer(all_tw_set ~ as.factor(set_num) + (1|Bat_ID) , data = subset_tia1, family= "poisson")
summary(tia_desc_glm)
# boxplot
tia_tib_tia_plot<- boxplot(all_tw_set ~ (as.factor(set_num)), main = "tia_tib_tia", data=subset_tia1)
```

There is no apparent discrimination between individual tungaras. 

## Summary chart


| trial_name | descrim? |dishabit? | comments
|:----------|------|------|-------------------------------------------|
|de_t_de  | no | no | probably bc no habituation in first place |
|t_de_t | no |no | probably bc high overall responses, low habit |
|ra_t_ta |yes, strong | yes | model failed to converge tho |
|t_ra_t | no | no | model didn't converge, failed hessian? |
|rra_rt_rra | yes, strong | no |  |
|rt_rra_rt | yes | no |  |
|tc_ts_tc |no |no |  crazy outlier to deal with, possbily no habituation|
|ts_tc_ts | yes | no | more clear bc better habituation|
| tia_tib_tia | no | no | not even at all. should have habituated too |


###Verbal explanation of discrimination results

Habituated fastest to Rhinella, followed by the reversed rhinella, followed by all the simple and one chuck tungaras, followed by the dendropsophes and the complex tungara, which they habituated to least. 
Consistent with expectations. 
	- Habituated faster to less biologically relevent simuli
	- But could it be that they didn't habituate to dendropsophes bc initial interest was so low, and there wasn't much of a place to habituate to? Depends on initial interest to TC, with second highest slope. If ithe initial interest is higher, and they still didn't habituate, more suggestive of higher interest indicated by low habituation rates. Redo initial interest to check. 
	- Could also be that the groups that showed lower habituation rates only did so bc they had less initial interest, and there was a floor effect-- less downward interest space in which to move.
 Is there a difference between the interest scores during test 5? Or are they all basically 0:

##Investigating response to 5th set
 
```{r}
#investigating difs in response to 5th stimulus
# running glmer 
# using relevel to find the true value (intercept) for each variable, and what is significantly different from each variable. 
 attn_set_5 <- read.table("/Users/maydixon/Dropbox/Attention Project/R/attn_set5_only.txt", header=TRUE) #local      
      
attn_set_5$primary_stim<-factor(attn_set_5$primary_stim, ordered=FALSE)   #make it a factor so it can be ranked     
attn_set_5$primary_stim <- relevel(attn_set_5$primary_stim,"De") #MAKE DE REFERENCE
        nlme_5set_de_ref<- glmer(all_tw_set ~ primary_stim + (trial_number|Bat_ID), family= "poisson", data = attn_set_5)
        summary(nlme_5set_de_ref)
        
        
        attn_set_5$primary_stim <- relevel(attn_set_5$primary_stim,"Ra") #MAKE RA REFERENCE
        nlme_5set_ra_ref<- glmer(all_tw_set ~ primary_stim + (trial_number|Bat_ID), family= "poisson", data = attn_set_5)
        summary(nlme_5set_ra_ref)
        
        attn_set_5$primary_stim <- relevel(attn_set_5$primary_stim,"Rra") #MAKE RRA REFERENCE
        nlme_5set_rra_ref<- glmer(all_tw_set ~ primary_stim + (trial_number|Bat_ID), family= "poisson", data = attn_set_5)
        summary(nlme_5set_rra_ref)
        
        attn_set_5$primary_stim <- relevel(attn_set_5$primary_stim,"Rt") #MAKE RT REFERENCE
        nlme_5set_rt_ref<- glmer(all_tw_set ~ primary_stim + (trial_number|Bat_ID), family= "poisson", data = attn_set_5)
        summary(nlme_5set_rt_ref)
        
        attn_set_5$primary_stim <- relevel(attn_set_5$primary_stim,"Ts") #MAKE Ts REFERENCE
        nlme_5set_ts_ref<- glmer(all_tw_set ~ primary_stim + (trial_number|Bat_ID), family= "poisson", data = attn_set_5)
        summary(nlme_5set_ts_ref)
        
        attn_set_5$primary_stim <- relevel(attn_set_5$primary_stim,"T1c") #MAKE T1c REFERENCE
        nlme_5set_t1c_ref<- glmer(all_tw_set ~ primary_stim + (trial_number|Bat_ID), family= "poisson", data = attn_set_5)
        summary(nlme_5set_t1c_ref)
        
        attn_set_5$primary_stim <- relevel(attn_set_5$primary_stim,"T2c") #MAKE T2c REFERENCE
        nlme_5set_t2c_ref<- glmer(all_tw_set ~ primary_stim + (trial_number|Bat_ID), family= "poisson", data = attn_set_5)
        summary(nlme_5set_t2c_ref)
        #
        
        
        
#reordering for plotting: 
      attn_set_5$primary_stim <- factor(attn_set_5$primary_stim,levels = c("Ts" ,"T1c", "T2c" , "De","Rt" , "Ra" , "Rra"),ordered = TRUE)
      
#perhaps best order is: Ts, T, Tc, Rt, Rra, Ra, De, can do using relevel() commands from above
```

##Plotting set 5
```{r}
      #plots
      library(plotly)
      #attn_set_5$md_lg_tw_set<- attn_set_5$md_tw_set + attn_set_5$lg_tw_set
#with logged +1 (for zero) data
p <- ggplot(data = attn_set_5, aes(x = primary_stim, y = log(all_tw_set+1), fill=primary_stim))
p <- p + geom_boxplot()
p <- p + geom_point(position = position_jitter(width = 0.1))
p <- p + theme(axis.text.x = element_text(angle = 90), legend.position = "none") #format x-axis, and remove side legend
p <- p + xlab("Acoustic stimuli")
p <- p + ylab("log( twitches in set 5 + 1)")
p
gg<-ggplotly(p)
``` 
#Summary chart
| stim           | value_est |	sig_vals |
| :--------------|-----------|------|
|De|	1.4648|	a|
|t2c|	1.3472|	ab|
|t1c|	0.7578|	cd|
|ts|	0.776	| bcd|
|rt|	0.5023|	d|
|rra|	-0.7505|	e|
|ra|	-0.8318|	e|



---




