---
title: "predictions_attention"
author: "may"
date: "June 29, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Predictions

1. comparing models with and without intercepts, with call as grouping and with set as grouping. 
```{r}
library(lme4)
mm1<- glmer(all_tw_call ~ call_num + call_num:trial_name_2 + (trial_number| Bat_ID), data= attn_habit_3, family="poisson") #run model
smm1<- summary(mm1)  #make summary
smm1
mm1a<- glmer(all_tw_call ~ call_num_2 + call_num_2:trial_name_2 + (trial_number| Bat_ID), data= attn_habit_3, family="poisson") #trying model with a different coding of call number. 
smm1a<- summary(mm1a)  #make summary
smm1a

mm1b <- glmer(all_tw_call ~ call_num  + trial_name_2 + call_num:trial_name_2 + (trial_number| Bat_ID), data= attn_habit_3, family="poisson") #with trial_name_2 as main effect
smm1b<- summary(mm1b)  #make summary
smm1b

mm1c <- glmer(all_tw_call ~ call_num  + trial_name_2 + call_num:trial_name_2 - 1 + (trial_number| Bat_ID), data= attn_habit_3, family="poisson") #run model with trial name as main effect and no intercept
smm1c<- summary(mm1c)  #make summary
smm1c

mm1d <- glmer(all_tw_call ~ call_num  + primary_stim + call_num:primary_stim + (trial_number| Bat_ID), data= attn_habit_3, family="poisson") #run model
smm1d<- summary(mm1d)  #make summary
smm1d # model with trial as main effect, no intercept, primary stim as group 

mm1e <- glmer(all_tw_call ~ call_num  + primary_stim + call_num:primary_stim + (1| Bat_ID), data= attn_habit_3, family="poisson") #run model
smm1e<- summary(mm1d)  #make summary
smm1e # same as mm1d but w/o trial number to see effect on hessian convergence


mm1_5<- glmer(all_tw_call ~ call_num + call_num:trial_name_2 -1 + (trial_number| Bat_ID), data= attn_habit_3, family="poisson") #run model
smm1_5<- summary(mm1_5)  #make summary
smm1_5  #

mm1epsilon <- glmer(all_tw_call ~ call_num  + primary_stim + call_num:primary_stim + (1| Bat_ID), data= attn_habit_3, family="poisson")
smm1epsilon<- summary(mm1epsilon)  #make summary
smm1epsilon
#######Ok, trying to fix hessian convergence issues. 
#try to scale numeric predictors (don't think this will work for me but whatever)
#so I am centering the call numbers around 0 and making the variance normal. 
attn_habit_3$scaled_call_num<- scale(attn_habit_3$call_num, center=TRUE, scale=TRUE)  #scaling call number
plot(attn_habit_3$scaled_call_num, attn_habit_3$call_num)

#also going to center call_num_2, which won't have the weird gaps that are weird
attn_habit_3$scaled_call_num_2<- scale(attn_habit_3$call_num_2, center=TRUE, scale=TRUE)  #scaling call number
plot(attn_habit_3$scaled_call_num_2, attn_habit_3$call_num_2) #this one won't have weird arbitrary gaps

#run model with scaled numeric variable, using 1.1...1.5 call_num scale
mm1f <- glmer(all_tw_call ~ scaled_call_num  + primary_stim + scaled_call_num:primary_stim + (1| Bat_ID), data= attn_habit_3, family="poisson")
smm1f<- summary(mm1f)  #make summary
smm1f

#run model with regular integer scale
mm1g <- glmer(all_tw_call ~ scaled_call_num_2  + primary_stim + scaled_call_num_2:primary_stim + (1| Bat_ID), data= attn_habit_3, family="poisson") #run model with scaled numeric variable, using scaled call nums from 1-~35 scale
smm1g<- summary(mm1g)  #make summary
smm1g

#run model with the  regular integer call num scale, this time without intercepts
mm1h <- glmer(all_tw_call ~ scaled_call_num  + primary_stim + scaled_call_num:primary_stim -1 + (1| Bat_ID), data= attn_habit_3, family="poisson") #run model with scaled numeric variable, using scaled call nums from 1.1...1.5 scale
smm1h<- summary(mm1h)  #make summary
smm1h

## So basically, scaling the call number to normal does help just a little bit, and is generally a good thing to do. 
#BUt still not converging, what if I add trial_number back in (full model)
#run model with the  decimal call num scale, this time without intercepts:

mm1i <- glmer(all_tw_call ~ scaled_call_num  + primary_stim + scaled_call_num:primary_stim -1 + (trial_number| Bat_ID), data= attn_habit_3, family="poisson") #run model with scaled numeric variable, using scaled call nums from 1.1...1.5 scale
smm1i<- summary(mm1i)
smm1i

#and with integer scale?    VVVVVVVVVVVVV

mm1j <- glmer(all_tw_call ~ scaled_call_num_2  + primary_stim + scaled_call_num_2:primary_stim -1 + (trial_number| Bat_ID), data= attn_habit_3, family="poisson") #run model with scaled numeric variable, using scaled call nums from integer scale
mm1i <-glmer(all_tw_call ~ scaled_call_num_2  + primary_stim + scaled_call_num_2:primary_stim + (trial_number| Bat_ID))
smm1i<- summary(mm1i)            
smm1j<- summary(mm1j)
smm1j
anova(mm1j) # This just demonstrates that is appropriate to further look for an interaction between  call number and primary stimulus. 

effects(scaled_call_num_2*primary_stim, mm1j) #this isn't called right
## This is the best model
## It is a full model, has all the main effects of call number and of the interaction effects
## It has both trial number and subject as random effects
## It converges
## It's "time" value is normalized and scaled (centered, etc), which is good bc the names for time are arbitrary anyway
## We used the call number scale that makes the most sense, isn't interpreted as different weights of differences between each chunk. 



## This is just for me to look at what the values of the slope are for the interactions:
smm1jnames<- rownames(smm1j$coefficients)
Estimate1<- smm1j$coefficients + smm1j$coefficients[1,1] #adding the main effect of call number, using De as reference. 
cbind(smm1jnames, as.numeric(Estimate1))


##Hookay. So now I have a model with some values that are things. I can try to estimate the confidence intervals now, I believe. 
#These are estimated confindence intervals:
confint_full_model<- confint(mm1j, type="bca")
CFM<- confint_full_model

#Now to make a dataframe with the fixed effect values of the interactions, and their confidence intervals

#now I am going to try to make a dataframe including only the interaction effects, and really, only the interaction effects when added to the reference value, so the true values of each of the interactions
# fixef_mm1j <- cbind(fixef(mm1j))
# fixef_mm1j_ie<-rbind(fixef_mm1j[1,],cbind(fixef_mm1j[9:14,] + fixef_mm1j[1,])) #deleting the no interaction effect fixed effects
# colnames(fixef_mm1j_ie)<- "fixeffects"
# fixef_mm1j_ie     
#       
# #Doing the same to the confidence intervals
# conf_frame<-rbind(CFM[4,], (CFM[12:17,] + CFM[4,])) #making all interactions true values by adding the main effect of call number which is referenced to de to the other values
# rownames(conf_frame)[1]<- "scaled_call_num_2:primary_stimde" #adding rowname to the first column
# TMT<-c("De", "Ra", "Rra", "Rt1c", "T1c", "T2c", "Ts") 
# row.names(conf_frame)<-NULL
# interaction_cis<-as.data.frame(cbind(TMT, fixef_mm1j_ie, conf_frame)) #data frame with the 95%cis for the interactions bectween call number and treatments
# interaction_cis$`2.5 %`<-as.numeric(as.character(interaction_cis$`2.5 %`))
# interaction_cis$`97.5 %`<-as.numeric(as.character(interaction_cis$`97.5 %`))
# interaction_cis$fixeffects<-as.numeric(as.character(interaction_cis$fixeffects))
# colnames(interaction_cis)<- c("TMT", "fixeffects", "lower_ci", "upper_ci")
# interaction_cis$midval<- apply(interaction_cis[,3:4],1, mean)
# row.names(interaction_cis) <- NULL 
# interaction_cis


### Alternatively, just use Tidy?
Mm1j_tidy<- tidy(mm1j, conf.int=TRUE)
#makes lovely dataframe with all my lovely values

#cleaning a bit:
MM1j_ceoffs<- Mm1j_tidy[-2:-8,]
MM1j_coeffss<- MM1j_ceoffs[-8:-10,]
MM1j_coeff3<- cbind(TMT, MM1j_coeffss)

#now to adjust for reference value. Make new columns adding reference to the interactions

MM1j_coeff3$slopes<- MM1j_coeff3[,3] + 0.05044288 #adding value of De/reference to the slopes
MM1j_coeff3$slopes[1]<-0.05044288 #fixing the effect for de
MM1j_coeff3$conf.low.adj<-MM1j_coeff3$conf.low + 0.05044288 #adding value of De/reference to the low.ci
MM1j_coeff3$conf.low.adj[1]<- -0.08649563 #fixing high ci for de

MM1j_coeff3$conf.high.adj<-MM1j_coeff3$conf.high + 0.05044288 #adding value of De/reference to the low.ci
MM1j_coeff3$conf.high.adj[1]<- 0.1873814 #fixing high ci for de

```
Now to graph these

```{r}
#graphing the slopes and their CI's

plot_ci_slopes<- ggplot(data= MM1j_coeff3, aes(x=TMT, y= slopes)) +
geom_point() +
geom_errorbar(ymin = MM1j_coeff3$conf.low.adj  , ymax = MM1j_coeff3$conf.high.adj )
plot_ci_slopes

plot_ci_slopes<- ggplot(data=interaction_cis,  aes(x=(lower_ci+upper_ci/2))) +
geom_errorbar(ymin = interaction_cis$lower_ci  , ymax = interaction_cis$upper_ci )

plot_ci_slopes
```
Show in New WindowClear OutputExpand/Collapse Output
estimate
<dbl>
std.error
<dbl>
statistic
<dbl>
p.value
<dbl>
conf.low
<dbl>
conf.high
<dbl>
group
<chr>
0.05044288	0.06986787	0.7219753	4.703096e-01	-0.08649563	0.1873814	fixed
-1.07186301	0.12024991	-8.9136282	4.938922e-19	-1.30754850	-0.8361775	fixed
-0.86674770	0.09873082	-8.7788968	1.650859e-18	-1.06025655	-0.6732388	fixed
-0.41473021	0.10785571	-3.8452320	1.204385e-04	-0.62612350	-0.2033369	fixed
-0.25967210	0.08068247	-3.2184451	1.288877e-03	-0.41780684	-0.1015374	fixed
-0.17686792	0.09734415	-1.8169343	6.922717e-02	-0.36765894	0.0139231	fixed
-0.36817611	0.10992532	-3.3493293	8.100745e-04	-0.58362578	-0.1527264	fixed
7 rows | 3-9 of 8 columns

##################
mm2<- glmer(all_tw_call ~ call_num + call_num:trial_name_2 + (1| Bat_ID), data= attn_habit_3, family="poisson") #run model
smm2<- summary(mm2)  #make summary
smm2

mm2_5<- glmer(all_tw_call ~ call_num + call_num:trial_name_2 -1+ (1| Bat_ID), data= attn_habit_3, family="poisson") #run model
smm2_5<- summary(mm2_5)  #make summary
smm2_5


mm3<- glmer(all_tw_set ~ set_num + set_num:trial_name_2 + (trial_number| Bat_ID), data= attn_habit_3, family="poisson") #run model
smm3<- summary(mm3)  #make summary
smm3

mm3_5<- glmer(all_tw_set ~ set_num + set_num:trial_name_2 -1 + (trial_number| Bat_ID), data= attn_habit_3, family="poisson") #run model
smm3_5<- summary(mm3_5)  #make summary
smm3_5

mm4<- glmer(all_tw_set ~ set_num + set_num:trial_name_2 + (1| Bat_ID), data= attn_habit_3, family="poisson") #run model
smm4<- summary(mm4)  #make summary
smm4


mm4_5<- glmer(all_tw_set ~ set_num + set_num:trial_name_2 -1 + (1| Bat_ID), data= attn_habit_3, family="poisson") #run model
smm4_5<- summary(mm4_5)  #make summary
smm4_5

mm5<- glmer(all_tw_set ~ set_num:trial_name_2 -1 + (trial_number| Bat_ID), data= attn_habit_3, family="poisson") #run model
smm5<- summary(mm5)  #make summary    #interaction only model
smm5



names<-c("smm1$AICtab", "smm1_5$AICtab", "smm2$AICtab", "smm2_5$AICtab", "smm3$AICtab", "smm3_5$AICtab", "smm4$AICtab", "smm4_5$AICtab, "smm5")
AIC_comp<- rbind( smm1$AICtab, smm1_5$AICtab, smm2$AICtab, smm2_5$AICtab, smm3$AICtab, smm3_5$AICtab, smm4$AICtab, smm4_5$AICtab, smm5)
AIC_comp<- cbind(names, AIC_comp)
AIC_comp

coeff_comp<- cbind(smm1$coefficients, smm1_5$coefficients, smm2$coefficients, smm2_5$coefficients, smm3$coefficients, smm3_5$coefficients, smm4$coefficients, smm4_5$coefficients)
coeff_comp




```



```{r}
library(lme4)
library(boot)
#2.5 #this adds call number as a main effect, but doesn't include the main effect of trial type
m2_5<- glmer(all_tw_call ~ call_num + call_num:trial_name_2 + trial_number + (1| Bat_ID), data= attn_habit_3, family="poisson")
sm25<- summary(m2_5)
sm25

boot_habit<-bootMer(x=sm25,FUN=fixef,nsim=200)
boot.ci(b_par,type="perc",index=1)




```